### 2022-05-17 manuscript.Rmd
Merge split reference sections again

bibliography_main    : "manuscript_files/main.bib"
bibliography_methods : "manuscript_files/methods.bib"
csl                  : "manuscript_files/nature.csl"
citeproc             : false

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"

output:
  papaja::apa6_pdf:
    pandoc_args: "--lua-filter=manuscript_files/multiple-bibliographies.lua"

@@

::: {#refs_main}
:::

\newpage
\linenumbers

@@

# Methods references

@@

::: {#refs_methods}
:::

\newpage
\linenumbers

@@

M.A.S. conceived, designed, and obtained funding for the study. A.E., S.K., and A.-S.K. (in consultation with M.A.S.) designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results. A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.

@@

The authors declare no competing interests.

# Additional information

Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).

>>>>

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/nature.csl"

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : "papaja::apa6_pdf"

@@

@@

@@

<div id="refs"></div>

@@

\noindent M.A.S. conceived, designed, and obtained funding for the study. A.E., S.K., and A.-S.K. (in consultation with M.A.S.) designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results. A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.

@@

\noindent The authors declare no competing interests.

# Materials & Correspondence

\noindent Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
